Results

### 2025-04-09 notebooks/00_index.qmd
feat: data reading

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
using GLMakie
using Statistics
# using CairoMakie
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend
using SPEDAS.SpaceDataModel: set

@@

```{julia}
using NCDatasets
using YAXArrays
path = "data/psp_e07.nc"
# ds = NCDataset(path)
ds = YAXArrays.open_dataset(path)
```

@@

psp_B_mva = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
psp_V_mva = Product("mva_V", (psp_V, psp_B), mva_transform; ylabel=V_ylabel, labels=mva_V_labels)

event = psp_events[2, :]
plot_candidate(event, [tvars_psp; [psp_B_mva, psp_V_mva]])
```

@@

>>>>

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
using GLMakie
using Statistics
# using CairoMakie
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend
using SPEDAS.SpaceDataModel: set
include("../src/psp_temp.jl")

@@

@@

psp_B_mva = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
psp_V_mva = Product((psp_V, psp_B), mva_transform; ylabel=V_ylabel, labels=mva_V_labels)
psp_eTemp_ani = Product(read_electron_temperature(), tview; labels=["Electron (parallel)", "Electron (perpendicular)"])
psp_pTemp_ani = Product(read_proton_temperature(), tview; labels=["Proton (parallel)", "Proton (perpendicular)"])
psp_Temp_ani = [psp_eTemp_ani, psp_pTemp_ani]

event = psp_events[2, :]
plot_candidate(event, [tvars_psp; [psp_B_mva, psp_V_mva, psp_Temp_ani]])
```

@@

```{julia}
